### 2022-07-19 chapters/benchmarking/draft.tex
Proof reading

Furthermore, between the exploratory experiment and the published results, there may have been the appearance of new candidates as well as the evolution of others.
As a result, it is not only necessary to ensure the "reproducibility" of the results, but it is also essential to provide room for new candidates.
As a result, we'd like to present "Extension," a new approach for leveraging experimentation.
The ability to give not only the tools needed to replicate the tests but also to integrate more candidates, workloads, or important key performance indicators

This chapter covers ways to overcome empirical analysis challenges in energy consumption studies. First, we  go through the three components of a successful benchmark within the energy consumption experiment. Section~\ref{sec:benchmarking_reproducibility}  therefore concentrates on the "reproducibility" issue and how to deliver reproducible experiments without interfering with the energy measurement. Section~\ref{sec:taming-the-energy-variation}  discusses accuracy in software energy consumption. 
Finally, Section~\ref{sec:bench_extension} presents tools for introducing new candidates, workloads, or other key performance indicators.

@@

\subsection{Docker \& Energy}
Now that we've decided to use container technology to enclose our tests, what effect will this have on the amount of energy our tests use?
%%%%%%%%%

Using research from \cite{santos2018does} who examined how adding the Docker layer affected energy consumption. \citeauthor{santos2018does}~\emph{et~ al} conducted their experiment by running numerous benchmarks both with and without Ddocker. They contrasted the energy usage and execution time that resulted.
The first step was to observe the effects of the orchestrator and the Docker deamon while there was no work to be done.
Then, they use three benchmarks in their experiments: Wordpress, Reddis and PostgreSQL.
The values below show the system under test's energy consumption while it is idle.
Docker has an overhead of roughly $1,000$  joules, as seen in Figure~\ref{fig:docker_idle} .

>>>>

Furthermore, between the exploratory experiment and the published results, there may have been the appearance of new candidates as well as the evolution of others.
As a result, it is not only necessary to ensure the "reproducibility" of the results, but it is also essential to provide room for new candidates.
As a result, we'd like to present "Extension", a new approach for leveraging experimentation.
The ability to give not only the tools needed to replicate the tests but also to integrate more candidates, workloads, or important key performance indicators

This chapter covers ways to overcome empirical analysis challenges in energy consumption studies. First, we go through the three components of a successful benchmark within the energy consumption experiment. Section~\ref{sec:benchmarking_reproducibility} concentrates on the "reproducibility" issue and how to deliver reproducible experiments without interfering with the energy measurement. Section~\ref{sec:taming-the-energy-variation} discusses accuracy in software energy consumption. 
Finally, Section~\ref{sec:bench_extension} presents tools for introducing new candidates, workloads, or other key performance indicators.

@@

\subsection{Docker \& Energy}
Now that we have decided to use container technology to enclose our tests, what effect will this have on the amount of energy our tests use?
%%%%%%%%%

Using research from \cite{santos2018does} who examined how adding the Docker layer affected energy consumption. \citeauthor{santos2018does} conducted their experiment by running numerous benchmarks both with and without Ddocker. They contrasted the energy usage and execution time that resulted.
The first step was to observe the effects of the orchestrator and the Docker deamon while there was no work to be done.
Then, they use three benchmarks in their experiments: Wordpress, Reddis and PostgreSQL.
The values below show the system under test's energy consumption while it is idle.
Docker has an overhead of roughly $1,000$  joules, as seen in Figure~\ref{fig:docker_idle} .
